### 2017-05-29 paper.tex
Fixing typos

The first requirement for building lessons together is
to know who they are being built for.
``Archaeology students'' is far too vague:
are you and your collaborators thinking of
first-year students who need an introduction to the field,
graduate students who intend to specialize in the sub-discipline which is the lesson's focus,
or someone in betwee?
Prerequisite knowledge,
equipment or software required,
how much time learners will actually have:
if different contributors believe different things about these,
they will find it difficult or impossible to work together.

@@

Lessons don't maintain themelves. 
Unlike traditional academic work, 
which may have shelf time measured 
in years (if not longer), 
technical lessons do not maintain themselves. 
Versions change, dependencies break, 
and what was cutting edge in 2017 may be dated 
and less useful in 2018. 
This needs to be clear to contributors, 
so they understand that this lesson is just 
the starting point. 
Sustainability needs to be front of mind.

The focus accordingly needs to be on creating a community. 
Authors cannot be expected to maintain continual vigilence on a lesson,
but this is necessary if one expectes continual use of a lesson! 
By working online, creating opportunities for collaboration 
and contribution, many eyes can keep the lesson usable. 
As we note below, 
this only works if you make space for 
little contributions just as you do for larger ones.

@@

Decades of pedagogical research has yielded many insights into
how best to build and deliver lessons \cite{hlw}.
Unfortunately,
since most college and university faculty have little or no training in education,
this knowledge and expertise is rarely transfered into classroom practice.

@@

If there are several complementary ways to explain something,
or several points of views that can cohabit respectfully,
it may be possible to present them side by side.
There are actualy good pedagogical reasons to do this even if contributors *don't* disagree:
weighing alternatives fosters higher-order thinking,
and as Caulfield has written,
the most popular online question and answer sites
are successful in part because they present a chorus of explanations
geared at different levels and needs
rather than a single one (FIXME: cite choral explanations).

>>>>

The first requirement for building lessons together is
to know who they are being built for.
``Archaeology students'' is far too vague:
are you and your collaborators thinking of
first-year students who need an introduction to the field,
graduate students who intend to specialize in the sub-discipline which is the lesson's focus,
or someone in between?
Prerequisite knowledge,
equipment or software required,
how much time learners will actually have:
if different contributors believe different things about these,
they will find it difficult or impossible to work together.

@@

Lessons don't maintain themselves. 
Unlike traditional academic work, 
which may have shelf time measured 
in years (if not longer), 
technical lessons do not maintain themselves. 
Versions change, dependencies break, 
and what was cutting edge in 2017 may be dated 
and less useful in 2018. 
This needs to be clear to contributors, 
so they understand that this lesson is just 
the starting point. 
Sustainability needs to be front of mind.

The focus accordingly needs to be on creating a community. 
Authors cannot be expected to maintain continual vigilance on a lesson,
but this is necessary if one expects continual use of a lesson! 
By working online, creating opportunities for collaboration 
and contribution, many eyes can keep the lesson usable. 
As we note below, 
this only works if you make space for 
little contributions just as you do for larger ones.

@@

Decades of pedagogical research has yielded many insights into
how best to build and deliver lessons \cite{hlw}.
Unfortunately,
since most college and university faculty have little or no training in education,
this knowledge and expertise is rarely transferred into classroom practice.

@@

If there are several complementary ways to explain something,
or several points of views that can cohabit respectfully,
it may be possible to present them side by side.
There are actually good pedagogical reasons to do this even if contributors *don't* disagree:
weighing alternatives fosters higher-order thinking,
and as Caulfield has written,
the most popular online question and answer sites
are successful in part because they present a chorus of explanations
geared at different levels and needs
rather than a single one (FIXME: cite choral explanations).
